APIs for hyperparameter optimization in scikit-learn

### 2013-05-13 paper.tex
tone down criticism of CPython

At this point in time, support for multi-core programming in Python,
at least in the CPython reference implementation targeted by scikit-learn,
is downright weak.
The interpreter supports multithreading, but due to the ``Global Interpreter Lock'' (GIL),
no two threads in a process may at the same time execute Python code.
It follows that multithreading is not a viable solution
even two embarrassingly parallel problems,
such as fitting and evaluation multiple models in a grid search procedure.
The workaround is to use Python's multiprocessing module,
which emulates threads using multiple operating system-level processes,
but this in turn leads to high memory use and overhead
because of the copying of training and test sets
into the various processes' address spaces.\footnote{
  The fact that copying occurs at all is an artifact of NumPy's implementation;
  no attempt at implementing a multiprocessing module
  that shares NumPy arrays using copy-on-write semantics or memory mapping
  has so far been completed.}

>>>>

At this point in time, support for multi-core programming in Python,
at least in the CPython reference implementation targeted by scikit-learn,
is one of the weak spots in the language and its libraries.
The interpreter supports multithreading,
but due to the ``Global Interpreter Lock'' (GIL),
no two threads in a process may at the same time execute Python code.
It follows that multithreading is not a viable solution
even two embarrassingly parallel problems,
such as fitting and evaluating multiple models in a grid search procedure.
The workaround is to use Python's multiprocessing module,
which emulates threads using multiple operating system-level processes,
but this in turn leads to high memory use and overhead
because of the copying of training and test sets
into the various processes' address spaces.\footnote{
  The fact that copying occurs at all is an artifact of NumPy's implementation;
  no attempt at implementing a multiprocessing module
  that shares NumPy arrays using copy-on-write semantics or memory mapping
  has so far been completed.}
